Galois Slicing as Differentiation

### 2025-07-11 main/introduction.tex
Start on intro.

Existing approaches to program slicing are often tied to particular programming languages or implementations. In this paper we develop a general categorical approach to program slicing and \todo{complete}.

>>>>

Existing approaches to program slicing are often tied to particular programming languages or implementations.
In this paper we develop a general categorical approach to program slicing, focusing on a particular technique
called \GPS, where the forward and backward slicing procedures for a particular execution form a Galois
connection. Our main insight is that this approach to slicing can be seen as a generalised form of
differentiable programming, with approximations (slices) of elements playing the role of tangents.
